Meta analysis of reprocessed RNASeq data from AMP-AD for hg38 Reprocessed Data (all 7 brain regions)

### 2021-11-17 code/RNA-Seq_Meta_Analysis.Rmd
New version RNA-Seq Weights

```{r libs, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
## It is assumed your working directory is where this file
## Load required libraries
library(CovariateAnalysis)
library(data.table)
library(plyr)
library(tidyverse)
library(knitr)
library(githubr)
library(doParallel)
library(foreach)
#cl = makeCluster(detectCores()-2)
#registerDoParallel(cl)
options(xtable.type="html")
knitr::opts_chunk$set(
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  cache = TRUE)
```

>>>>

```{r libs, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
## It is assumed your working directory is where this file
## Load required libraries
library(CovariateAnalysis)
library(data.table)
library(plyr)
library(tidyverse)
library(knitr)
library(githubr)
library(doParallel)
library(foreach)

options(xtable.type="html")
knitr::opts_chunk$set(
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  cache = TRUE)
```
